---
title: "odd_R"
author: "LW"
date: "2026-01-14"
output: html_document
---
## 6.3 Some R-code
In order to demonstrate the creation of an R-package, we will identify some odd behaviour by R:
```{r}
c(0.5, 1.5, 2.5, 3.5) |> round()
```

We can see that R rounds - by default - the number 1.5 to integer 2 and the number 2.5 also to integer 2. The reason for this behaviour is the IEC 60559 standard where a 5 is expected to be rounded to the even digit.

If we’d like to round up to the next integer, we can easily define the following function:
```{r}
rounder <- function(x){
  diff <- x - floor(x)
  out <- ceiling(x)
  out[diff < .5] <- floor(x)[diff < .5]
  return(out)
}
```

where the vector c(0.5, 1.5, 2.5, 3.5) is rounded up to the next integer
```{r}
c(0.5, 1.5, 2.5, 3.5) |> rounder()
```

and where the vector c(0.49, 1.49, 2.49, 3.49) is rounded down to the previous integer
```{r}
c(0.49, 1.49, 2.49, 3.49) |> rounder()
```

## 6.4 Create R-package roundR
### 6.4.1 Steps in creating an R-package

We need the following packages to help us with building, testing and maintaining our package:
```{r}
library(devtools) # development tools
library(usethis)  # automated package and project setup
library(testthat) # unit testing
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

